Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
paper: tweak experiments section

The queries consist not only of projections and selections, but also
interesting joins and aggregates. Our aim was to craft meaningful queries that would
provide performance figures relevant to practitioners using similar datasets.
\review{
Our benchmark queries performed well for both cases of \texttt{AVG} and \texttt{COUNT} aggregates, 
so we expect \ProjectName{} would provide similar performance for \texttt{SUM}, with 
errors proportional to the fraction of relevant tuples retrieved and the \texttt{AVG} value estimated.}

@@

%\begin{figure}
%\includegraphics[width=\columnwidth]{figures/planning_times_imputedb.png}
%\caption{Planning times for each query}
%\label{fig:plantimes}
%\end{figure}
\textbf{Accuracy vs. Base-table Imputation (AVG)}\quad \Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results compared to the baseline, using the reference chained-equation decision trees model.
This measures the error introduced by on-the-fly imputation as compared to full imputation on the base tables.
This comparison is the relevant one in practice --- an analyst would only be considering the trade-offs in imputation quality and time in the first place for dirty input data, for which ground truth is unavailable.

@@

\textbf{Alternate Imputation Methods}\quad
We also experiment with mean-value imputation and hot deck imputation
(\Cref{sec:imputation}). In our implementation of mean-value imputation, to facilitate
non-blocking operation within the iterator model, we estimate the column mean from base
table histograms. Therefore, imputed values are identical no matter where the operator is
placed in the query plan (relative errors are $0$). Runtimes are in the range of
\runtimemeanlow{} to \runtimemeanhigh{} for queries using \ProjectName{}, as compared to
\runtimemeanlowbase{} to \runtimemeanhighbase{} when imputing on the base table.  Here, the
time cost of the imputation is relatively low no matter how many tuples need to be imputed.

>>>>

The queries consist not only of projections and selections, but also
interesting joins and aggregates. Our aim was to craft meaningful queries that would
provide performance figures relevant to practitioners using similar datasets.
\review{
Our benchmark queries performed well for both cases of \texttt{AVG} and \texttt{COUNT} aggregates, 
so we expect \ProjectName{} to perform similarly for \texttt{SUM}, with 
errors proportional to the fraction of relevant tuples retrieved and the \texttt{AVG} value estimated.}

@@

%\begin{figure}
%\includegraphics[width=\columnwidth]{figures/planning_times_imputedb.png}
%\caption{Planning times for each query}
%\label{fig:plantimes}
%\end{figure}

\textbf{Accuracy vs. Base-table Imputation (AVG)}\quad \Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results compared to the baseline, using the reference chained-equation decision trees model.
This measures the error introduced by on-the-fly imputation as compared to full imputation on the base tables.
This comparison is the relevant one in practice --- an analyst would only be considering the trade-offs in imputation quality and time in the first place for dirty input data, for which ground truth is unavailable.

@@

\textbf{Alternate Imputation Methods}\quad
We also experiment with mean-value imputation and hot deck imputation
(\Cref{sec:imputation}). In our implementation of mean-value imputation, to facilitate
non-blocking operation within the iterator model, we estimate the column mean from base
table histograms. Therefore, imputed values are identical no matter where the operator is
placed in the query plan (relative errors are $0$). Runtimes are in the range of
\runtimemeanlow{} to \runtimemeanhigh{} for queries using \ProjectName{}, as compared to
\runtimemeanlowbase{} to \runtimemeanhighbase{} when imputing on the base table.  Here, the
time cost of the imputation is low no matter how many tuples need to be imputed.
